%----------------------------------------------------------
% begin song latex formating, set the title and other info

\beginsong{Viste Quando}
[
    id                     = {16},
    psalterio_number       = {16},
    music_by               = {},
    lyrics_by              = {},
    arrangement_by         = {},
    bible_verse            = {},
    licence_or_copyright   = {},
    video_url              = {},
    extra                  = {},
    index                  = {Viste Quando},
]

%----------------------------------------------------------
% section #1: verse 

\beginverse

\[Eb]Viste quando o Se\[Bb]nhor \[Cm]mo\[Gm]rreu \[Bb7]na c\[Eb]ruz?
Viste \[Gm]quan\[Bb]do o Se\[Cm]nhor mo\[Bb]rreu \[Eb]na c\[Bb]ruz?
\[Eb]Oh! \[Ab]As \[Eb]ve\[Ab]zes \[Eb]tenho \[G]pena e\[Cm] tremo,\[Ab] tremo, tr\[Eb]emo,\[Ab Bb]
\[Ab]Viste \[Eb]quando o Se\[Bb]nhor \[Cm]mo\[Gm]rreu n\[Bb7]a cr\[Eb]uz?

\endverse

%----------------------------------------------------------
% section #2: verse 

\beginverse

\[Eb]Viste quando O pre\[Bb]ga\[Cm]ram\[Gm] nu\[Bb7]ma c\[Eb]ruz?
Viste \[Gm]quan\[Bb]do O pre\[Cm]garam\[Bb] nu\[Eb]ma c\[Bb]ruz?
\[Eb]Oh! \[Ab]As \[Eb]ve\[Ab]zes \[Eb]tenho \[G]pena e\[Cm] tremo,\[Ab] tremo, tr\[Eb]emo,\[Ab Bb]
\[Ab]Viste \[Eb]quando O pre\[Bb]ga\[Cm]ram\[Gm] nu\[Bb7]ma c\[Eb]ruz?

\endverse

%----------------------------------------------------------
% section #3: verse 

\beginverse

\[Eb]Viste quando p'ra \[Bb]tum\[Cm]ba \[Gm]foi \[Bb7]Je\[Eb]sus?
Viste \[Gm]quan\[Bb]do p'ra \[Cm]tumba \[Bb]foi \[Eb]Je\[Bb]sus?
\[Eb]Oh! \[Ab]As \[Eb]ve\[Ab]zes \[Eb]tenho \[G]pena e\[Cm] tremo,\[Ab] tremo, tr\[Eb]emo,\[Ab Bb]
\[Ab]Viste \[Eb]quando p'ra \[Bb]tum\[Cm]ba \[Gm]foi \[Bb7]Je\[Eb]sus?

\endverse

%----------------------------------------------------------
% section #4: verse 

\beginverse

\[Eb]Viste quando o Se\[Bb]nhor \[Cm]re\[Gm]ssus\[Bb7]ci\[Eb]tou?
Viste \[Gm]quan\[Bb]do o Se\[Cm]nhor re\[Bb]ssus\[Eb]ci\[Bb]tou?
\[Eb]Oh! \[Ab]As \[Eb]ve\[Ab]zes \[Eb]tenho \[G]pena e\[Cm] tremo,\[Ab] tremo, tr\[Eb]emo,\[Ab Bb]
\[Ab]Viste \[Eb]quando o Se\[Bb]nhor \[Cm]re\[Gm]ssus\[Bb7]ci\[Eb]tou?

\endverse





%----------------------------------------------------------
% end song

\endsong
