%----------------------------------------------------------
% refer to template.tex to see how to edit this file 
\beginsong{Follow Me}
[
    id                  = {480},
    music_by            = {Rui Ferreira}, % Music Author
    lyrics_by           = {Rui Ferreira}, % Lyrics Author
    arrangement_by      = {}, % Arrangement Author
    bible_verse         = {},
    licence_or_copyright= {},
    sr                  = {},
    cr                  = {},
    video_url           = {}, % vimeo, facebook, etc. (for youtube videos use the youtube_id
    youtube_id          = {}, % example: https://www.youtube.com/watch?v=7km1-BSWgeg
    music_score         = {https://musescore.com/user/26352/scores/11871820}, % example: https://musescore.com/user/26352/scores/7572545
    extra               = {EUD Camporee 2023 Theme Song},
    index               = {Follow Me},
]

%----------------------------------------------------------
\beginverse
Intro\[C F C F C]

\[C]Here I go, I'm no longer the same
\[F]Left my path, when You called my name
\[C]You’re the Light, always guiding my way\[F]
You are \[Am]Jesus\[G]
\endverse
%----------------------------------------------------------
\beginverse
\[C]I have peace, one the world cannot give
\[F]I won’t fear, I will trust, I'll believe
\[C]Times might change, but your love will remain\[F]
You are \[Am]Je-\[G]sus
\endverse
%----------------------------------------------------------
\beginverse
\[C]No turning back, no giving up\[F]
I'll lift my voice, I'll shout it out\[C]
Through highs and lows, there's victory\[F]
\[Am]Won't you \[G]come and \[F]see?
\endverse
%----------------------------------------------------------
\beginchorus
\[C]Fol\[C/E]low \[F]Me, \[Am]I’m the Way, the \[Gsus4]Truth, the Li\[G]fe
\[C]Fol\[C/E]low \[F]Me, \[Am]I am always \[Gsus4]by your si\[G]de
\[C]Fol\[C/E]low \[F]Me… comparte tu historia,
\[C]Se\[C/E]gui\[F]mi… vorbește-Mi despre tine
\[C]Násle\[C/E]duj \[F]mě… 
\[Am]Won't you \[G]come and \[F]see?
Follow Me\[C F C]
\endchorus

%----------------------------------------------------------
\beginverse
\[C]Joy and hope, I can't keep to myself
\[F]I will go, I've a story to tell
\[C]Come along, share this journey with me\[F]
Come meet \[Am]Je\[G]sus
\endverse
%----------------------------------------------------------
\beginverse
\[C]No turning back, no giving up\[F]
I'll lift my voice, I'll shout it out\[C]
Through highs and lows, there's victory\[F]
\[Am]Won't you \[G]come and \[F]see?
\endverse

%----------------------------------------------------------
\beginchorus
\[C]Fol\[C/E]low \[F]Me, \[Am]I’m the Way, the \[Gsus4]Truth, the Li\[G]fe
\[C]Fol\[C/E]low \[F]Me, \[Am]I am always \[Gsus4]by your si\[G]de
\[C]Fol\[C/E]ge \[F]mir... partage ton histoire
\[C]Se\[C/E]gue-me... deel je verhaal
\[C]Sle\[C/E]dvay \[F]me...
\[Am]Won't you \[G]come and \[F]see?
\[Am]Won't you \[G]come and \[F]see?
Follow Me\[C]
\endchorus

%----------------------------------------------------------
\endsong
