%----------------------------------------------------------
% begin song latex formating, set the title and other info

\beginsong{Dios es Amor}
[
    id = {330},
    psalterio_number = {330},
    music_by = {Azarías Bull, Manuel Lillo & Juan M. Fustero},
    lyrics_by = {},
    arrangement_by = {},
    bible_verse = {},
    licence_or_copyright = {},
    video_url = {},
    extra = {},
    index = {},
]

%----------------------------------------------------------
% section #1: verse 

\beginverse

Quiero escri\[A]bir una canci\[E]ón
que \[Bm]todo el mundo \[D]pueda enten\[E]der.
Con una \[A]voz y un solo i\[E]dioma, que con \[Bm]una sola \[D]nota
yo \[Bm]pueda descri\[D]bir tu gran am\[E]or.
Quiero gri\[A]tar al mundo en\[E]tero
que en mi \[C#m]vida eres más que especi\[D]al;
que tú controlas \[Bm]todo, cada \[D]parte de \[E]mí.

\endverse

%----------------------------------------------------------
% section #2: chorus

\beginchorus

\[A]Dios es amor, my \[E]God is love.
Déu és \[F#m]amor, nasha san gôn\[E]gô.
Dio è amo\[Bm]re, Dieu est \[E]amour.
\[A]Deus é amor, \[E]Gott ist Lieben.
Is é Dia\[F#m]grá, Kami wa aidea\[E]ru.
Bog uest lyub\[Bm]ov, Dewa cin\[E]ta.

\endchorus

%----------------------------------------------------------
% section #3: verse 

\beginverse
I want to sing a special song,
a song that everybody understands.
Only one voice, only one language.
Describing your love, God,
opening my heart with just one note.
I want to shout to the whole world
the things you've done in my life,
that you are there controlling every part of my soul.
\endverse


%----------------------------------------------------------
% section #4: verse 

\beginverse
Y haré\[D] entender que er\[A]es amor,
\[D]desde el norte \[A]hasta el sur,
a ca\[Bm]da pueblo, l\[D]engua y cada nac\[E]ión.
\endverse
%----------------------------------------------------------
% end song

\endsong
